\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-24 paper/paper.tex
Small edits to computation paragraph. Remove reference to effective sample sizes.

\subsection{Computation}
\label{sec:Computation}
Each model was fit using the {\tt
  rstan}\cite{rstan} package in {\tt R} \cite{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\cite{betancourt}. HMC jointly updates all model parameters by simulating energy preserving paths with random initial momentums along the posterior density. This is done to reduce autocorrelation and efficiently explore the posterior. Multiple chains were run for 1500 iterations after 1500 warmup iterations: 4 chains were run for Models 1,2 and 3 and 16 chains were run for Model 4. The Gelman-Rubin potential scale reduction factors, ``R-hat", which test for lack of convergence by comparing the between versus within chain variability were used. Upon convergence, R-hat converges to 1. For the four model fits, the  maximum values over all 140 model parameters were 1.005, 1.028, 1.009 and 1.004, respectively. The minimum estimated effective sample size over the model parameters were 567, 205, 672 and 3330 for Models 1 through 4, respectively. No divergent transitions occurred after warmup.

>>>>

\subsection{Computation}
\label{sec:Computation}
Each model was fit using the {\tt
  rstan}\cite{rstan} package in {\tt R} \cite{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\cite{betancourt}. HMC jointly updates all model parameters by simulating energy preserving paths with random initial momentums along the posterior density. This is done to reduce autocorrelation and efficiently explore the posterior. Multiple chains were run for 1500 iterations after 1500 warmup iterations: 4 chains were run for Models 1,2 and 3 and 16 chains were run for Model 4. The Gelman-Rubin potential scale reduction factor was used to provide a check for adequate mixing of the multiple chains. Upon convergence, $\hat{R}$, converges to 1. The number of model parameters for the four model fits are . The  maximum values of $\hat{R}$ across all model parameters for Models 1 throught 4 (5, 50, 95 and 140 parameters, respectively) were 1.005, 1.028, 1.009 and 1.004. Other diagnostics provided by the software (tree-depth, and divergent transitions) were clean. Plots of the posterior draws were inspected for parameters with the fewest effective samples; these did not suggest features that were inadequately explored.
